%        File: wm_2013_nuc.tex
%     Created: Mon Aug 13 10:00 AM 2012 C
%
\documentclass[letterpaper]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[usenames]{color}
\usepackage[
naturalnames = true, 
colorlinks = true, 
linkcolor = Black,
anchorcolor = Black,
citecolor = Black,
menucolor = Black,
urlcolor = Blue
]{hyperref}
\def\thesection       {\arabic{section}}
\def\thesubsection     {\thesection.\alph{subsection}}

%% To use the glossaries acronym package, you'll need to define any acronyms you intend to 
%% use. You can define acronyms with \newacronym{label}[acronym]{written out form}
%% To refer to them in the text use \gls{label}
\usepackage[acronym,toc]{glossaries}
\makeglossaries

\author{Kathryn D. Huff
\\ \href{mailto:khuff@anl.gov}{\texttt{khuff@anl.gov}}
\\ 9700 S. Cass Ave
}

\date{}

% concise yet adequately descriptive title
\title{Hydrologic Nuclide Transport Models in Cyder, A Geologic Disposal Software Library}
\begin{document}
\maketitle

\input{acros}


% 1) a descriptive title that will reflect the paper 
%    and presentation content (define all acronyms); 
% 2) a summary of the work conducted, 
%    problem history and your results; 
% 3) all authors contact information including mailing address, email addresses and phone 
%    numbers; and 
% 4) a brief description of the importance of the work 
%    (what problem it addresises/solves) and its application/benefit to others.  


% Abstracts should be between 400 - 800 words and comply with the 
% criteria stated below. Results have shown that brief abstracts that fully and 
% effectively convey the substance and their importance have the highest 
% ranking. Background information irrelevant to an abstract’s merits may 
% dilute the substance and lower the ranking. The evaluation criteria on the 
% “Abstract Rating Form” is posted on the WM website www.wmsym.org
% under the Presenters tab as a guide for authors. Insufficient information 
% for the reviewers may result in session misplacement, lower ranking or 
% abstract rejection.

% Some analytical models have been created for cyder, many levels of detail 
% % Degradation Rate
% % Mixed Cell 
% % Lumped Param
% % OneDimPPM
% Some sensitivity analyses have been conducted to improve the speed 
% % gdsm
% % what params
% %  
% % 
% They've been implemented in a flexible, modular way. 


% 2. How is the technical problem, issue or program and its importance clearly described?                    
% 3. How are the results or likely results of the investigation/solutions(s) to the problem or 
%    issue described?
%    5 - Very clearly described and supported
%    4 - Above-average
%    3 - Average and somewhat unfocused in specific details
%    2 - Below-average
%    1 - Abstract lacks a clear issue, focus and/or results
% 4. What is the significance of the work/results described?               
%    4 - Significant and widely applicable
%    3 - Applicable to a previously difficult or specific problem or issue resolution
%    2 - Incremental improvement to/status update of an already solved problem      
%    1 –Addresses an already resolved problem     
%    0 - Addresses no known or significant problem or issue by the reviewer
%5. Is the work original and new or an expansion of prior work?             
%    2 – Presents new work/results or new insight
%    1 - Effectively builds on previous work/results
%    0 - Nothing significantly new in work, program, issue resolution or results
%6. How is the information discussed likely to be of interest to attendees? 
%    4 - Will provide an excellent presentation and be a benefit to attendees
%    3 - Will provide an above-average presentation
%    2 - Will result in an average presentation
%    1 - Will be a below-average presentation
%7. Total of the Individual Reviewer’s Scores

\section{Work Conducted}
% Provide a summary of the work conducted:
%      Describe the technical problem clearly
%      support it with a method

This work describes four hydrologic radionuclide transport models that resulted from 
the abstraction of more detailed tools. A proof of principle demonstration of their 
application will also be discussed in which they were used to represent 
the natural and engineered barrier components of a repository concept in a 
reducing, homogenous, generic geology. Finally, the integration of these models 
with a fuel cycle simulation platform will be described.

Component level and system level abstraction of detailed computational geologic 
repository models has resulted in four rapid computational models of 
hydrologic radionuclide transport at varying levels of detail. These abstracted 
models have been implemented in Cyder, a software library of interchangeable 
radionuclide transport models appropriate for representing natural and 
engineered barrier components of generic geology repository concepts.
Cyder is an open source library intended for integration with the 
Cyclus Fuel Cycle Simulator, but with an interface suitable for linking to other 
tools or for use as a stand-alone radionuclide transport calculation engine. 

The Cyder software library under development integrates with 
the Cyclus computational fuel cycle systems analysis platform in order to 
calculate repository performance metrics with respect to candidate fuel cycle 
options \cite{huff_cyder_2012,huff_cyclus:_2010}. By abstraction of more 
detailed geological nuclide transport models, Cyder aims to capture the dominant 
physics of radionuclide transport phenomena affecting repository performance in 
various geologic media and as a function of spent fuel composition.

\section{Motivation}
% Provide a brief description of the importance of the work (what problem it 
%   addresses/solves):
Radionuclide containment behavior of a geologic repository is a strong function 
of spent fuel composition, which varies among alternative fuel cycles. For this 
reason, a generic disposal model capable of integration with a systems analysis 
framework is necessary to illuminate performance distinctions of candidate 
repository geologies, designs, and engineering components in the context of fuel 
cycle options. 

A generic repository model appropriate for systems analysis must emphasize 
modularity and speed while providing modeling options at various levels of 
detail. Sensitivity analyses and abstraction efforts conducted to develop the 
models described in this work sought to capture the dominant physics of detailed 
repository behaviors so that abstracted models can be robustly and flexibly 
implemented in the Cyder disposal environment library without sacrificing the 
simulation speed required by the Cyclus fuel cycle simulator.

\section{Results}
% Provide your results:
%       clearly

The results of this work consist of four models that are the product of an 
abstraction effort with more detailed tools. Results of unit tests and 
benchmarking efforts will be described as will a proof of principle base case 
demonstration of the use of these models. The base case concept has used these 
tools to model a generic, isotropic, permeable porous geological medium with 
reducing geochemistry as well as waste form, waste package, and buffer models in 
the near field.

The analytic models modified by abstraction and implemented in Cyder include a 
degradation rate model, a mixed cell model, a response function model, and a 
one dimensional solution (Brenner, 1962) to the advection-dispersion equation.

The degradation rate model simulates the fractional degradation of the material 
containment properties is the simplest of implemented models and is most 
appropriate for simplistic waste package failure modeling. 

Slightly more complex, and suited to representating waste form and buffer 
components, the mixed cell model incorporates solubility limited, congruent 
release under the influence of elemental partitioning coefficients and diffusion 
coefficients as well as advective velocity. Abstraction results concerning the 
transition between primarily diffusive and primarily advective transport regimes 
was used for benchmarking and iterative accuracy improvements in the development 
of this model.

The lumped parameter, response function model implemented interchangeable piston flow, 
exponential, and dispersion response functions and was developed by direct 
calibration against the results of the abstraction effort.  

Finally, abstraction results informed modifications implementation of an 
analytic solution to the one dimensional advection-dispersion equation with 
finite domain and Cauchy and Neumann boundary conditions at the inner and outer 
boundaries, respectively. 

\section{Importance to Others}

The Cyder source code in which these models are implemented as well as 
associated documentation are freely available for use by model developers in the 
field of nuclear waste management. The application programming interface to this 
software library is intentionally general to facilitate the incorporation of the 
models presented here within software tools in need of a multicomponent repository 
model.

Furthermore, this work contributes to an expanding ecosystem of computational 
models available for use with the Cyclus fuel cycle simulator. This hydrologic 
nuclide transport library, by virtue of its capability to modularly integrate 
with the Cyclus fuel cycle simulator has laid the foundation for integrated 
disposal option analysis in the context of fuel cycle options. 

\end{document}


